---
author: "`r params$school`"
return-address: "`r params$full_address`"

params:  
  first_name: "Caely" 
  last_name: "Aguilera Sanchez"
  full_name: "Caely Aguilera Sanchez"
  principal_name: "Laura English"
  school: "La Mirada Elementary"
  full_address: "222 Avenida de la Madrid San Ysidro CA 92173-1508"
  pronoun: her
  day_abs: 9
  times: 5

subject: ABSENCES MATTER AND YOU CAN HELP
opening: Dear Parent/Guardian of `r params$full_name`, 
closing: Best regards,
signature: "`r params$principal_name`, Principal"

output: komaletter::komaletter
---

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(here)
library(ggplot2)
library(lubridate)

#https://github.com/rnuske/komaletter/blob/master/vignettes/parameterized_letter.Rmd
```

```{r data, echo=FALSE}
personalized_info <-  readRDS(here("data", "processed", "results_factor_nov_up_san.rds")) %>%
  filter(date == as.Date("2021-11-01"))

principal <- readRDS(here("output", "results", "principal.rds"))
```

```{r transform-tidy-data, echo=FALSE}
# select columns for letter; add principals
personalized_info_select <- personalized_info %>%
  select(first_name, last_name, gender, school, exp_att_day, day_abs, pct_abs, date)

# calculate median for schools  
personalized_info_median <- personalized_info %>%
  filter(!is.na(day_abs)) %>%
           group_by(school) %>%
           summarize(median_days = round(mean(day_abs, na.rm = FALSE), digits = 0)) %>%
           ungroup()

# merge median back into 1st dataset
personalized_info_merge <- personalized_info %>%
  left_join(personalized_info_median, median_days, by = "school")

# mutate merged dataset
personalized_info_mutate <- personalized_info_merge %>%
  mutate(times = (day_abs - median_days)) %>%
  mutate(pronoun = ifelse(gender == "M", "his", "her")) %>%
  filter(times > 0)

# mutate join column because something funky is going on
personalized_info_mutate_school <- personalized_info_mutate %>%
  mutate(school_2 = substr(school, 1, 5))
  
principal_school <- principal %>%
  mutate(school = ifelse(school == "Howard Pence Elementary", "Pence Elementary", principal$school),
         school_2 = substr(school, 1, 5))

# join tables
personalized_info_mutate_2 <- personalized_info_mutate_school %>%
  fuzzyjoin::fuzzy_join(principal_school, match_fun = str_detect, by = "school_2", mode = "left") %>%
  select(last_name, first_name, school = school.x, median_days, times, day_abs, pronoun,
         mail_street, mail_city, mail_state, mail_zip, phone, adm_f_name, adm_l_name,
         adm_email)

# check matches
#personalized_info_mutate_school %>%
  #fuzzyjoin::fuzzy_join(principal_school, match_fun = str_detect, by = "school_2", mode = "anti") %>%
  #count(school)
```


```{r letter-vectors, echo=FALSE}
# need to change this # params$first_name

personalized_info_mutate_3 <- personalized_info_mutate_2 %>%
  unite("full_name", c("first_name", "last_name"), sep = " ", remove = F) %>%
  unite("full_address", c("mail_street":"mail_zip"), sep = " ", 
                 remove = F) %>%
  unite("principal_name", c("adm_f_name":"adm_l_name"),
                   sep = " ", remove = T) %>%
  mutate(full_name = as.factor(full_name))
rm(list = c("personalized_info", "personalized_info_median",
            "personalized_info_merge", "personalized_info_mutate", "personalized_info_mutate_2",
            "personalized_info_select"))

saveRDS(personalized_info_mutate_3, file = here("output", "results", "nudge_san.rds"))
```

`r params$first_name` has missed more school than `r params$pronoun` classmates.* 

`r params$first_name` has already missed `r params$day_abs` days this school year. 

Students fall behind when they miss school – whether students are absent for excused or unexcused reasons. 

You can have a big effect on `r params$first_name`’s absences going forward – and we appreciate your help.

```{r abs-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=2}
abs_plot <- personalized_info_mutate_3 %>%
  filter(full_name == params$full_name) %>%
  reshape2::melt(.) %>%
  filter(variable %in% c("day_abs", "median_days"))

ggplot(data = abs_plot,
       mapping = aes(x = variable, y = value, fill = variable)) +
  geom_col(position = "dodge") +
  coord_flip() +
  scale_x_discrete(label = c("Typical Student", params$first_name)) +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  scale_fill_manual(values=c("#404788FF", "#FDE725FF")) +
  labs(y = "Total Missed Days of School", 
       x = "") +
  theme_classic() +
  theme(legend.position="none") + theme(axis.ticks = element_line(size = 1)) +labs(x = NULL)
```


*`r params$first_name` has missed `r params$times` more school days than `r params$pronoun` classmates this school year.
